
\chapter{The Comordo recommender system}\label{cha:recsys}

This chapter describes the background of the thesis and the task given by given by Comordo for the construction of the recommender system which is the main purpose of the thesis from Comordo's point of view. Then a rundown of mathematical theory of the used recommendation model and description of the used algorithms follow.

%Then background theory about supervised learning, the used recommendation model and evaluating recommendations and a summary of optimization strategies are given.  Descriptions of the algorithms \textit{katz-eig} and \textit{link-analysis} follow.

Comordo Technologies is a startup in recommendation systems driven inside the bounds of LiU's incubator LEAD in Linköping and will in the future offer a cloud service for e-commerce. The base for the recommendation system is algorithms based on predication and machine learning. At the start of this thesis the company stood to build a first version of it's recommendation system.

Comordo focuses on generating personal recommendations using \textit{implicit feedback} aimed at e-commerce using purchase history for users as their main focus. The end product aims to be a remote API where e-commerce clients queries for precomputed recommendations made for their users.

\Warning[TODO]{ Stich together }

This chapter presents the development methodology used, then the datasets used and finally the evaluation method for evaluating recommendation quality are presented.

The thesis can be split in two major parts. A system development part where a first version of Commordo's recommender system is built, the ``glue'' around the recommender algorithms. The second part with development of a learning framework for the algorithms and an analysis of the algorithms' parameters.

The focus on the beginning is on the system development part and with that in place the focus shiftes to the learning framework and parameter tuning.

\input{recsys/dev}
\input{recsys/evaluation}

\input{recsys/use_case.tex}
\input{recsys/system_overview.tex}
\input{recsys/task.tex}

\input{recsys/system}
\newpage
