\chapter{Results}\label{cha:Results}

\textit{Pure facts and as objectively as possible. Don't analyze, comment or evaluate.  If describe implementation process, only describe largest decisions.}

\input{results/system}
\newpage

\input{results/data}
\newpage

\Warning[TODO]{Reformat and reformulate graphs etc}

\input{results/learning_curves.tex}
\newpage

\input{results/training_curves.tex}
\newpage

\input{results/katzeig.tex}
\newpage

\input{results/linkanalysis.tex}
\newpage




\section{Big comparisons?}
\Warning[TODO]{ title? Where? What? How? :) }

Compare katz-eig, link-analysis, and some other algorithm?
Also compare optimization w.r.t. time and evaluation.

\begin{enumerate}
    \item Running time
    \item F-measure
\end{enumerate}


\textit{Unsure about the rest!}

\section{Optimization}\label{sec:res:opt}

Optimization techniques in broad stroaks.

Resulting graphs from LinkAnalysis. Use different kinds of datasets.

\begin{itemize}
    \item Graph over $\gamma$ with fixed $\eta$.
    \item Graph over $\eta$ with fixed $\gamma$.
    \item Graph over $\gamma$, $\eta$.
    \item Graph over $T$, see that things flattens out.
\end{itemize}

Similarly for KatzEig.


Compare custom\_neighbour, custom\_neighbour\_step, fminsearch, ... with each other. Compare runtime and accuracy over different kinds of datasets.

Similarly for KatzEig.



\subsection{Julia}\label{subsec:res:julia}

\Warning[TODO]{ Move to discussion? Conclusions? }

Although not a focus of this thesis, some explorations with Julia has been undertaken.


%\begin{chapter-appendix}
%
%\section{Ett par långa bevis}
%
%Det här är en appendix-del av det aktuella kapitlet.
%
%\end{chapter-appendix}

