
\section{Motivation}\label{sec:intro:motivation}

Being able to choose has always been an important skill and perhaps it's more important now than ever before. It's hard to choose what products to buy, what music to listen to, what posts to read and what videos to watch as there are many choices. In Youtube alone over 300 hours of video is uploaded every minute \textit{(ref needed)}.

This is why content providers and e-commerce are using recommendations, where products believed to appeal to the consumer are presented more prominently on the sites. Recommendations have become an important part of their business and companies such as Netflix are investing heavily into making their recommendations better \textit{(ref needed)}.

A common practice among e-commerce is to produce related recommendations where products are linked to related, similar, products. Another type is personal recommendations where products are recommended specifically for a single user given their purchase or interaction history.

\vspace{1cm}

Describe the problem and make it clear that it's interesting and important to study closer. Make the reader interested.

In the modern day, data collection is growing more and more prevalent. Search providers or social media like Google and Facebook are obvious examples, their whole existence is built on data collection and aggregation, but it's prevalent in other services as well. Your local store or cinema will often have a record of your purchase history, not because it's their purpose to track you, but it's a byproduct of you purchasing things from them. Websites may check what links you click and what sites you came from, and especially what ads you're clicking on.

This information, your purchase or interaction history, can be used to guess what you're interested in and can produce recommendations for you.

ref: \url{http://www.youtube.com/yt/press/statistics.html}

Related recommendations links related products together and personal recommendations recommends products based on your interaction history, for example if you're watching a lot of videos featuring cats you might be recommended other cat videos.
