
\section{Outline of the report}\label{sec:intro:outline}

This thesis consists of two parts. The first part concerns the system development part where a first version of Comordo's recommender system is built. The second part consists of an analysis of the parameter space and optimization strategies for the algorithms' parameters. The system development part is concentrated to chapter 4 and the parameter analysis to chapter 6.

\begin{description}
    \item[Chapter 2] introduces the mathematical background for the thesis. The recommendation model and the learning process along with the recommendation algorithms \textit{katz-eig} and \textit{link-analysis} are presented.
    \item[Chapter 3] discusses work related to this thesis.
    \item[Chapter 4] covers the system development part of this thesis. Beginning with the given system development task and then presenting the constructed recommender system.
    \item[Chapter 5] presents the datasets used by this thesis. Contains an analysis of the datasets with respect to interactions and clusters.
    \item[Chapter 6] covers the parameter analysis and optimization. The chapter begins with an analysis of the algorithms and the parameter space and finishes with a comparison of different optimization techniques and a comparison between the algorithms.
    \item[Chapter 7] contains a discussion about the thesis and presents ideas for future work. Recommender systems in general and the one built are discussed. Then discussion about the datasets, the evaluation method and finally parameter tuning follow.
    \item[Chapter 8] concludes with the conclusions of this thesis.
    \item[Appendix A] lists the optimized parameters for each dataset and algorithm.
    \item[Appendix B] presents the available source code. Only an example reader plugin is available.
    \item[Appendix C] describes the test setup used by this thesis.
\end{description}

